Staged typed type-preserving tagless ``interpreters'', \emph{finally}

### 2007-04-01 tagless/tagless-final.tex
re-re-re fix de Bruijn's name

The main tool is to take functions seriously: we encode the
de-Bruijn or higher-order abstract syntax  of object terms 
not by using constructors for
an algebraic data type but rather by invoking cogen functions, which occur as
free variables in the encoded term.  In other words, we eschew initial
algebras for the wilder world of final algebras.
(Or: we expose the co-algebraic structure of the object language).
Our approach highlights the importance of order-2 type constructors
(rank-2 polymorphism), available with ML functors and
Haskell98 constructor classes. This lets us encode object terms with
translucent types: enough abstraction is available to interpret the
terms in various ways, and yet enought type information is available 
to typecheck the terms and statically assure their interpretation will
never get stuck.

>>>>

The main tool is to take functions seriously: we encode the
de Bruijn or higher-order abstract syntax  of object terms 
not by using constructors for
an algebraic data type but rather by invoking cogen functions, which occur as
free variables in the encoded term.  In other words, we eschew initial
algebras for the wilder world of final algebras.
(Or: we expose the co-algebraic structure of the object language).
Our approach highlights the importance of order-2 type constructors
(rank-2 polymorphism), available with ML functors and
Haskell98 constructor classes. This lets us encode object terms with
translucent types: enough abstraction is available to interpret the
terms in various ways, and yet enought type information is available 
to typecheck the terms and statically assure their interpretation will
never get stuck.
